This final-year project focuses on the design and implementation of \textbf{PharmacieConnect}, a web and
mobile platform dedicated to Tunisian pharmacies, on-duty pharmacy schedules, and quick access to useful
information from a phone. The work starts from a practical observation: duty schedules are still shared
through heterogeneous lists that are not always easy to correct or search, while citizens often need this
information at night, during weekends, or on public holidays.

PharmacieConnect relies on three complementary components. The backend is the technical core of the
platform. With \textbf{FastAPI}, it brings together data access, business rules, REST endpoints, and
security mechanisms based on JWT authentication, roles, and regional scopes. On the administration side,
the \textbf{React}/\textbf{Vite} dashboard is used to maintain pharmacies, duty schedules, medicines,
authorized users, CSV imports, analytics, and audit logs. The mobile application uses \textbf{Expo}
and \textbf{React Native} and covers citizens' main journeys: text search, on-duty schedule consultation
by date, geolocation, medicine catalog access, and a first-aid conversational assistant.

The project is not limited to visible interfaces. It also addresses several software engineering concerns,
including data modeling with SQLAlchemy, input validation, role-based access control, audit logging,
backend testing, and a clear separation between client interfaces, business services, and data
persistence. The first-aid assistant adds a hybrid information retrieval layer, evaluated with retrieval
metrics and surrounded by safety messages whenever a situation requires medical attention.

\textbf{Keywords:} on-duty pharmacy, FastAPI, React, Vite, Expo, React Native, JWT, REST API,
SQLAlchemy, dashboard, mobile application, first-aid assistant.
